Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
color_redshift/redshift_vs_W1W2.py
tex/VHzQ.pdf

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
%
\citet{LaMassa2017, Glikman2018, LaMassa2019} 
%

@@

%%
%\subsubsection{Individual VH$z$Qs with Interesting MIR properties}

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 21 WFCAM and 12 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter and with the average calibrated flux is greater than 0 and at least $8\times$ the error on the average calibrated flux. 1 objects is in common to both, so this sample of 32 is our starting point for variability investigations. The common object is VIK J1148+0056. 
%% is SDSSJ0958+3524 special at all??

At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this. Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).

Then calculate the clipped median and standard deviation, 
\begin{equation}
1.48 \times \sigma_{median} / \bar{\epsilon}
\end{equation}
where $\bar{\epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
%%
With this definition, although some of the objects have very well sampled, 
`average' light curves where you are averaging over e.g. a month, or two weeks.

@@

%% 
%% Object numbers: 54 VSA   MMTJ0215-0529,
%% objID: 162 is both VSA and WSA and  SDSSJ0959+0227
%%

%% 
%% objiD 164 is SDSSJ1000+0234, faint; very faint. 
%% SHELLQsJ0220-0432: (qso59) show this too. 
%%

%%
%% CFHQSJ0216-0455
%%

\begin{figure}[H]
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
    \caption{MMTJ0215-0529}
    \label{fig:MMTJ0215-0529}
  \end{subfigure}%
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
    \caption{CFHQSJ0216-0455}
    \label{fig:CFHQSJ0216-0455}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SHELLQsJ0220-0432}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \medskip
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
several investigations have looked at how WISE detects AGN 
\citet[e.g][]{Secrest2015, Assef2015, Stern2015, Assef2018, LaMassa2017, Glikman2018, LaMassa2019}

@@

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, 
we select objects with at least 8
measurements observed with durations over 30 days, in at least one
filter and with the average calibrated flux is greater than 0 and at
least $8\times$ the error on the average calibrated flux. 
%At least 8 original observations across at least 30 days in either WSA or VSA per 
% band, calibrated flux greater than zero over the whole time, and the
% error on the average flux is 8 times lower than this. 
A requirement of SNR$>3$ per `average' epoch, where `average epoch' is
then dependent on the averaging timescales (which as we see can vary).
The clipped median and standard deviation is then calculated 
\begin{equation}
     1.48 \times \sigma_{median} / \bar{\epsilon}
\end{equation}
where $\bar{\epsilon}$ is the mean of the error in each point in the
light curve, divided by the total number of points.
%%
With this definition, although some of the objects have very well sampled 
with an ``average'' light curve sampling over e.g. a month, or two weeks. 
%%
With these criteria, there are 21 WFCAM and 12 VISTA objects 
with 1 object (VIK J1148+0056 ) in common to both, and this sample of 32 is our starting point for variability investigations.

We present four objects that are particularly well-sampled in the NIR; these are
MMTJ0215-0529 (Figure~\ref{fig:MMTJ0215-0529}), 
CFHQSJ0216-0455 (Figure~\ref{fig:CFHQSJ0216-0455}), 
SHELLQsJ0220-0432 (Figure~\ref{fig:SHELLQsJ0220-0432}) and 
SDSS J0959+0227 (Figure~\ref{fig:SDSS J0959+0227}). 
We also incorporate the MIR NEOWISE-R light data where available.

\begin{figure}
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
    \caption{MMT J0215-0529}
    \label{fig:MMTJ0215-0529}
  \end{subfigure} 
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
    \caption{CFHQS J0216-0455}
    \label{fig:CFHQSJ0216-0455}
  \end{subfigure}
\end{figure}

\begin{figure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SHELLQs J0220-0432}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SDSS J0959+0227}
    \label{fig:SDSSJ0959+0227}
  \end{subfigure}
  \medskip
\end{figure}

@@
